Refinements for open automata

### 2023-04-03 2021-Refinement/paper/refinementarticleV2.tex
add figures FIFO
add figures...
minor todo
ajout figures dans le tex
trvail sur les figures

\begin{example} As a running example, we consider a data base example inspired from \cite{Gorrieri:2001}. The open automaton \texttt{database}  modelling the behaviour of data base is depicted in Fig. \ref{Fig:SpecOA}. The \texttt{database} can be queried using an operation \texttt{qry} and updated using an operation \texttt{upd}. The associated automaton has a single hole:  a counter ($\texttt{cnt}$)  depicting  the behaviour of the timer. When the \texttt{database}  performs a query,  it sets the new time limit of the counter component and the exposed action to the environment is an observable  action \texttt{qry}.
The \texttt{database} updates and  switches when it agrees with the counter component the time is over, and the exposed action is \texttt{upd}.
The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig. \ref{Fig:counter}. 
\end{example}
\begin{figure}[h]
 \centering
   \includegraphics[width=.9\textwidth]{Figures/database.pdf}
   \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
 to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
\end{figure}

@@

\begin{figure}[h]
 \centering
   \includegraphics[width=.55\textwidth]{Figures/counter.pdf}\hfill 
   \includegraphics[width=.35\textwidth]{Figures/compose_count_db.pdf}
   \caption{(Left) Open Automaton of \texttt{counter} process.  Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart. (Right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
\end{figure}

@@

@@

@@

>>>>

\TODO{Debut Exemple-1}
\begin{example} As a running example, we consider a classical producer-consumer pair  with FIFO buffer. The overall structure shown in Fig. \ref{Fig:Architect}
reflects the different processes involved in the communication and all the actions performed.

\begin{figure}[h]
 \centering
   \includegraphics[width=.70\textwidth]{Figures/Architecture.pdf}
   \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
 to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:Architect}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
\end{figure}

The open automaton  modelling the behaviour of the \texttt{prod-cons}  system is depicted in Fig. \ref{Fig:SpecOA}. The \texttt{prod-cons} can be fed using an operation \texttt{push} and discharged  using an operation \texttt{pop}. The automata has two holes: $\texttt{P}$ and  $\texttt{Q}$  depicting  the behaviour of the producer and consumer resp. When the \texttt{prod-cons} agrees with $\texttt{P}$ on a data admission, it   stores the data in a local variable and  exposes to the environment an observable action \texttt{push}. At the opposite side, when it agrees with $\texttt{Q}$ on a data retrieval, it exposes  a \texttt{pop} action. It can also agree with $\texttt{Q}$ on admission of data but this one is rather printed not stored (\texttt{pop(m)}). 
Besides, producing and  consuming, it can agree on the computation action of both processes but this action is exposed as unobservable actions $\tau$.

\medskip

a data base example inspired from \cite{Gorrieri:2001}. The open automaton \texttt{database}  modelling the behaviour of data base is depicted in Fig. \ref{Fig:SpecOA}. The \texttt{database} can be queried using an operation \texttt{qry} and updated using an operation \texttt{upd}. The associated automaton has a single hole:  a counter ($\texttt{cnt}$)  depicting  the behaviour of the timer. When the \texttt{database}  performs a query,  it sets the new time limit of the counter component and the exposed action to the environment is an observable  action \texttt{qry}.
The \texttt{database} updates and  switches when it agrees with the counter component the time is over, and the exposed action is \texttt{upd}.
The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig. \ref{Fig:counter}. 
\end{example}
\begin{figure}[h]
 \centering
   \includegraphics[width=.95\textwidth]{Figures/FIFOpen2.pdf}
   \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
 to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
\end{figure}

@@

\begin{figure}[h]
 \centering
   \includegraphics[width=.35\textwidth]{Figures/P-proc.pdf}\hfill 
   \includegraphics[width=.45\textwidth]{Figures/Q-proc.pdf}
   \caption{(Left) Open Automaton of \texttt{counter} process.  Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart. (Right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
\end{figure}

@@

\TODO{parler de generalisation a la composition a n automates}

@@

\section{Example}
\TODO{A completer...}

\begin{figure}[!tb]
 \centering
   \includegraphics[width=.65\textwidth]{Figures/Architecture.pdf}
   \caption{\texttt{Archtecture du systeme}. \label{Fig:Archi}}
\end{figure}

\begin{figure}[!tb]
 \centering
   \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
   \caption{\texttt{FIFO} process.  Two other actions,  in addition to  \texttt{p-a} and \texttt{p-b},  \texttt{in} representing a     \texttt{out} are used to reflect the actual operation of copying. \label{Fig:FIFOA}}
\end{figure}

@@

\begin{figure}[!tb]
 \centering
   \includegraphics[width=1.25\textwidth]{Figures/FIFORing.pdf}
   \caption{\texttt{FIFO} process.  \label{Fig:RefineOA}}
\end{figure}

\begin{figure}[h]
 \centering
   \includegraphics[width=.40\textwidth]{Figures/P-proc.pdf}\hfill 
   \includegraphics[width=.55\textwidth]{Figures/Q-proc.pdf}
   \caption{(Left) Open Automaton of \texttt{P} process.   (Right) Open Automaton of  \texttt{Q} process.\label{Fig:processes}}
\end{figure}
